---
title: "R Notebook: 1 big function"
output: html_notebook
---

We previously made a couple of functions to extract the first goal minute, type of the first goal, formations of both teams...
We now want to wrap it in 1 function such that each link is only requested once to be more more efficient and avoid overloading the server. To do this we have to change the function input parameters from the link itself to the parsed HTML document. Later we make one general function with all functions combined. 
```{r}
library(rvest)
library(dplyr)
library(tidyverse)
library(janitor)
library(stringr)
library(purrr)
library(xml2)

# The 3 functions about the goals are combined in 1 function/
# Input is now the parsed HTML document, not the link for efficiency
get_first_goal_details_parsed <- function(match_page) {
  default_result <- list(
    minute = NA_real_,
    is_penalty = FALSE,
    is_owngoal = FALSE,
    team_id = NA_character_
  )

  if (is.null(match_page)) {
    message("DEBUG: match_page is NULL in get_first_goal_details_parsed. Direct default return.\n")
    return(default_result)
  }

  tryCatch({
    get_first_team_goal_details <- function(team_id) {
      team_selector <- paste0("div.event#", team_id)

      team_main_event <- match_page %>%
        html_element(paste0("#wrap #content .scorebox ", team_selector))

      if (is.null(team_main_event)) {
        return(default_result) 
      }

      first_goal_sub_event <- team_main_event %>%
        html_element(xpath = "./div[.//div[contains(concat(' ', @class, ' '), ' event_icon ') and (contains(concat(' ', @class, ' '), ' goal ') or contains(concat(' ', @class, ' '), ' penalty_goal ') or contains(concat(' ', @class, ' '), ' own_goal '))]]")

      if (is.null(first_goal_sub_event)) {
        return(default_result) 
      }

      event_text_raw <- first_goal_sub_event %>% html_text()
      minute_pattern <- "(\\d+\\+\\d+)|\\d+"
      goal_minute_raw <- str_extract(event_text_raw, minute_pattern)

      minute_val <- NA_real_
      if (!is.na(goal_minute_raw)) {
        m_clean <- str_remove(goal_minute_raw, "'$")
        if (str_detect(m_clean, "\\+")) {
          parts <- str_split(m_clean, "\\+")[[1]]
          base_minute <- as.numeric(parts[1])
          extra_minute <- NA_real_
          if (length(parts) > 1 && parts[2] != "") {
            extra_minute <- as.numeric(parts[2])
          }
          if (!is.na(base_minute) && base_minute == 90 && !is.na(extra_minute)) {
            minute_val <- base_minute + extra_minute
          } else {
            minute_val <- base_minute
          }
        } else {
          minute_val <- as.numeric(m_clean)
        }
      }

      icon_class <- first_goal_sub_event %>%
        html_node(xpath = ".//div[starts-with(concat(' ', @class, ' '), ' event_icon ')]") %>%
        html_attr("class")

      is_penalty_goal_val <- !is.na(icon_class) && str_detect(icon_class, "penalty_goal")
      is_own_goal_val <- !is.na(icon_class) && str_detect(icon_class, "own_goal")

      team_str <- if (team_id == "a") "Home" else "Away"

      return(list(
        minute = minute_val,
        is_penalty = is_penalty_goal_val,
        is_owngoal = is_own_goal_val,
        team_id = team_str
      ))
    }

    home_goal_details <- get_first_team_goal_details("a")
    away_goal_details <- get_first_team_goal_details("b")

    all_potential_first_goals <- list()
    if (!is.na(home_goal_details$minute)) {
      all_potential_first_goals[[length(all_potential_first_goals) + 1]] <- home_goal_details
    }
    if (!is.na(away_goal_details$minute)) {
      all_potential_first_goals[[length(all_potential_first_goals) + 1]] <- away_goal_details
    }

    if (length(all_potential_first_goals) == 0) {
      message("DEBUG: No goals found for either team. Returning default.\n")
      return(default_result)
    }

    minutes_vector <- purrr::map_dbl(all_potential_first_goals, "minute", .null = NA_real_)
    first_goal_idx <- which.min(minutes_vector)

    final_first_goal_data <- all_potential_first_goals[[first_goal_idx]]

    return(list(
      minute = final_first_goal_data$minute,
      is_penalty = final_first_goal_data$is_penalty,
      is_owngoal = final_first_goal_data$is_owngoal,
      team_id = final_first_goal_data$team_id
    ))

  }, error = function(e) {
    message(paste0("ERROR in get_first_goal_details_parsed: ", e$message, "\n"))
    return(default_result)
  })
}

test_link <- "https://fbref.com/en/matches/059136bc/Club-Brugge-Mechelen-July-26-2024-Belgian-Pro-League"
test_page <- read_html(test_link)
test_result <- get_first_goal_details_parsed(test_page)
# Test on other link: chech no goals
test_link2 <- "https://fbref.com/en/matches/5e117e2c/Dender-Union-SG-July-27-2024-Belgian-Pro-League"
test_page2 <- read_html(test_link2)
test_result2 <- get_first_goal_details_parsed(test_page2)
# Test 90+2 behaviour
test_link3 <- "https://fbref.com/en/matches/05f2ad6b/Anderlecht-Sint-Truiden-July-27-2024-Belgian-Pro-League"
test_page3 <- read_html(test_link3)
test_result3 <- get_first_goal_details_parsed(test_page3)
# Test penalty behaviour
test_link4 <- "https://fbref.com/en/matches/a41d3109/Mechelen-Westerlo-August-3-2024-Belgian-Pro-League"
test_page4 <- read_html(test_link4)
test_result4 <- get_first_goal_details_parsed(test_page4)
# Test own goal behaviour
test_link5 <- "https://fbref.com/en/matches/591ddbff/Antwerp-Anderlecht-August-4-2024-Belgian-Pro-League"
test_page5 <- read_html(test_link5)
test_result5 <- get_first_goal_details_parsed(test_page5)

```

Here we will write the get formation function. It will provide 
```{r}
# The get formation function is also changed, receiving parsed HTML
get_formation_parsed <- function(match_page) { 
  default_result <- list(
    home_formation = NA_character_,
    away_formation = NA_character_
  )

  if (is.null(match_page)) {
    return(default_result)
  }

  tryCatch({
    home_formation <- match_page %>%
      html_element("#wrap") %>%
      html_element("#content") %>%
      html_element("#field_wrap") %>%
      html_elements(".lineup#a") %>%
      html_element("table") %>%
      html_element("tr") %>%
      html_element("th") %>%
      html_text2()

    pattern <- "(\\d+-\\d+-\\d+(?:-\\d+)*)"
    home_formation <- str_extract(home_formation, pattern)

    away_formation <- match_page %>%
      html_element("#wrap") %>%
      html_element("#content") %>%
      html_element("#field_wrap") %>%
      html_elements(".lineup#b") %>%
      html_element("table") %>%
      html_element("tr") %>%
      html_element("th") %>%
      html_text2()

    away_formation <- str_extract(away_formation, pattern)

    return(list(
      home_formation = home_formation,
      away_formation = away_formation
    ))

  }, error = function(e) {
    message(paste0("ERROR in get_formation_parsed: ", e$message, "\n"))
    return(default_result)
  })
}
test_result_formation <- get_formation_parsed(test_page)
# Test on other link
test_result_formation2 <- get_formation_parsed(test_page2)

```

```{r}
# General function with all functions in 1.
get_full_match_details <- function(link) {
  default_full_result <- list(
    link = link,
    first_goal_minute = NA_real_,
    first_goal_is_penalty = FALSE,
    first_goal_is_owngoal = FALSE,
    team_id_first_goal = NA_character_,
    home_formation = NA_character_,
    away_formation = NA_character_,
    goal_scored = FALSE 
  )

 # Only one webrequest here
  match_page <- tryCatch({
    message(paste0("DEBUG: Load page: ", link, "\n"))
    read_html(link)
  }, error = function(e) {
    message(paste0("ERROR: Error loading page ", link, ": ", e$message, "\n"))
    Sys.sleep(sample(seq(1, 3, by = 0.1), 1)) 
    return(NULL) 
  })

  if (is.null(match_page)) {
    return(default_full_result)
  }

  Sys.sleep(sample(seq(3, 5, by = 0.1), 1))

  first_goal_data <- get_first_goal_details_parsed(match_page)

  formations_data <- get_formation_parsed(match_page)

  goal_scored <- !is.na(first_goal_data$minute) && first_goal_data$minute > 0

  final_result <- list(
    link = link,
    first_goal_minute = first_goal_data$minute,
    first_goal_is_penalty = first_goal_data$is_penalty,
    first_goal_is_owngoal = first_goal_data$is_owngoal,
    team_id_first_goal = first_goal_data$team_id,
    home_formation = formations_data$home_formation,
    away_formation = formations_data$away_formation,
    goal_scored = goal_scored
  )

  return(final_result)
}
# Test the function 
test <- get_full_match_details(test_link)
test2 <- get_full_match_details(test_link2)
test3 <- get_full_match_details(test_link3)
test4 <- get_full_match_details(test_link4)
test5 <- get_full_match_details(test_link5)
```

```{r}
# Add in delay for server
links_processed_in_batch_counter <- 0
get_full_match_details_with_delay <- function(link) {
  links_processed_in_batch_counter <<- links_processed_in_batch_counter + 1

  result <- get_full_match_details(link)

  if (links_processed_in_batch_counter %% 18 == 0) {
    cat(paste0("18 links processed. Wait 5 seconds...\n"))
    Sys.sleep(5)
  }
  return(result)
}
# Test
test_delay <- get_full_match_details_with_delay(test_link)
```

```{r}
# Perform batch processing in three or 4 parts. Best stay below 128 links at a time.
links_processed_in_batch_counter <- 0

df_matches_withlinks1 <- df_matches_withlinks |>
  slice(1:ceiling(nrow(df_matches_withlinks)/3)) # Takes row 1 to the last observation in 1/3th of the df
df_matches_withlinks2 <- df_matches_withlinks |>
  slice((ceiling(nrow(df_matches_withlinks)/3) + 1):(ceiling(nrow(df_matches_withlinks)/3) * 2)) # Takes row 1/3th to the last observation in 2/3th of the df
df_matches_withlinks3 <- df_matches_withlinks |>
  slice((ceiling(nrow(df_matches_withlinks)/3) * 2 + 1):nrow(df_matches_withlinks))

processed_df_list <- list()
for (j in 1:3) {
  current_df_part <- get(paste0("df_matches_withlinks", j))
  cat(paste0("\n\n--- Start processing part ", j, " ---\n"))
  
  links_processed_in_batch_counter <- 0

  links_to_scrape_in_part <- current_df_part %>% pull(link)

  scraped_full_data <- map_dfr(links_to_scrape_in_part, get_full_match_details_with_delay, .progress = TRUE)

  current_df_part <- current_df_part %>%
    left_join(scraped_full_data, by = "link")

  processed_df_list[[j]] <- current_df_part

  write_csv(current_df_part, paste0("df_matches_part", j, "_full_details_processed.csv"))
  cat(paste0("\nPart ", j, " Processed and saved.\n"))
}
# Combine all parts into one final dataframe
final_df <- bind_rows(processed_df_list)
```

